Characterization of gaps in directly bonded Si compound optics

### 2014-02-17 AO_bondedSi.tex
add section on spectra, begin the table of measurement outcomes

\subsection{Spectra of pucks with known gap sizes}
Figures \ref{1} to \ref{2} show examples of the predicted and measured IR spectra.  Figure \ref{1} shows

>>>>

\subsection{Spectra of pucks with known gap sizes}
Figures \ref{1} to \ref{2} show examples of the predicted and measured IR spectra.  Figure \ref{VS21specm1} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{VS21specf1} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 2 \sigma$).  Other parts show less consistency with the prediction.  A complete description of the diversity of the measured spectra requires an appeal to optical phenomena beyond the scope of this paper.  Briefly we classify the diversity of measurements into the categories laid out in the table below.

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posM1.eps}}
\caption{IR transmission spectrum of VS21 (M1) showing consistent gap\label{VS21specm1}.  Example spectrum through part VS21 at a position through the mesh gap of known dimensions.}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=.8\columnwidth]{figs/20130911_VS21posF1.eps}}
\caption{IR transmission spectrum of part VS21 (F1) showing evidence for an excess gap\label{VS21specf1}.  Example spectrum through part VS21 at a position through the mesh gap of known dimensions.}
\end{figure}
